### 2016-11-04 introduction.tex
more shit

Essentially, \cite{mozer1989using} observed that the behavior of neural networks during training is not to distribute the learning representation evenly or even equitably across hidden units. What actually happens is that a few, elite neurons learn an approximation of the input-output function, and the remaining units simply learn a complex interdependence function which cancels out their respective influence. Furthermore, assuming enough units exist to learn the function in question, increasing the number of parameters does not increase the richness or robustness of the learned approximation, but rather simply increases the number of noisy parameters to cancel. This is evinced by the fact that in many cases, whole neurons can be removed from a network with minimal to no impact on the output approximation, and even more so in the case of networks with copious extraneous units. In this sense, there are few bipartisan units in a trained network. A unit is typically either part of the input-output function approximation, or it is part of an elaborate noise cancellation task force. Assuming this is true, most of the compute-time spent training a neural network is likely occupied by this arguably wasteful procedure of silencing superfluous parameters, and pruning is thus part of a necessary treatment procedure to ``trim the fat''.

We observed this very same phenomenon in our experiments, and this is the motivation behind our decision to evaluate our algorithms on the criteria of their ability to trim neurons without any re-training. As \cite{fahlman1989cascade} discuss, the ``herd effect'' and ``moving target'' problems in back-propagation learning simply cause the remaining units in a network to shift course and What we discovered is that predicting the behavior of a network when a unit is to be pruned is very difficult, and

>>>>

Essentially, \cite{mozer1989using} observed that the behavior of neural networks during training is not to distribute the learning representation evenly or even equitably across hidden units. What actually happens is that a few, elite neurons learn an approximation of the input-output function, and the remaining units simply learn a complex interdependence function which cancels out their respective influence. Furthermore, assuming enough units exist to learn the function in question, increasing the number of parameters does not increase the richness or robustness of the learned approximation, but rather simply increases the number of noisy parameters to cancel. This is evinced by the fact that in many cases, whole neurons can be removed from a network with minimal to no impact on the output approximation, and even more so in the case of networks with copious extraneous units. In other words, there are few bipartisan units in a trained network. A unit is typically either part of the input-output function approximation, or it is part of an elaborate noise cancellation task force. Assuming this is true, most of the compute-time spent training a neural network is likely occupied by this arguably wasteful procedure of silencing superfluous parameters, and pruning is thus a necessary treatment procedure to ``trim the fat.''

We observed evidence of this phenomenon in our experiments, and this is the motivation behind our decision to evaluate our pruning algorithms on the simple criteria of their ability to trim neurons \textit{without} any re-training. If we were to employ re-training as part of our evaluation criteria, we would arguably \textit{not} be evaluating the quality of our algorithm's pruning decisions per se but rather the ability of back-propagation trained networks to recover from faults, as per (\cite{segee1991fault} \cite{mozer1989skeletonization}). As \cite{fahlman1989cascade} discuss, the ``herd effect'' and ``moving target'' problems in back-propagation learning will simply cause the remaining units in a network to shift course and re-learn whatever error signal is either re-introduced or forgotten as a result of a network fault. So long as a network has enough critical parameters to learn the function in question, a network can likely recover with additional training.

In terms of removing units without re-training, what we discovered is that predicting the behavior of a network when a unit is to be pruned is very difficult, and most of the approximation techniques put forth in existing pruning algorithms do not fare well at all when compared to a brute-force search. To begin our discussion of how we arrived at our algorithm and set up our experiments, we begin with a review of the existing literature.
